---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```
# Welcome to the dev-version of the 

#[library flipscores on CRAN](http://cran.r-project.org/web/packages/flipscores/index.html)


* * *

## Set up

To **install** this github version type (in R):

    ##if devtools is not installed yet: 
    ## install.packages("devtools") 
    library(devtools)
    install_github("livioivil/flipscores")


## Some examples

## Binomial

```{r,  message = FALSE}
library(flipscores)
set.seed(1)
x=(rep(0:1,20))
D=data.frame(y=rbinom(40,1,.25+x*.5), x=x,z=rnorm(40),id=rep(1:20,each=2))
mod_par=glm(y~x*z,data=D,family = binomial)
summary(mod_par)
mod_par
mod=flipscores(y~x*z,data=D,family = binomial, score_type = "effective")
summary(mod)
print(mod)

# with clustered observations:
mod=flipscores(y~x*z,data=D,family = binomial, id=D$id, score_type = "ort")
summary(mod)
```

## Poisson

```{r,  message = FALSE}
set.seed(1)
y=(sample(1:200,20))
x=(rep(0:1,20))
D=data.frame(y=y, x=rbinom(40,1,.25+x*.5), z=rnorm(40),id=rep(1:20,each=2))
mod_par=glm(y~x*z,data=D, family = poisson)
summary(mod_par)
mod=flipscores(y~x*z, data=D, family = poisson, score_type = "effective")
summary(mod)
```

## Linear model

```{r,  message = FALSE}
set.seed(1)
D$y=rnorm(40)
mod=flipscores(y~x*z, data=D, family = gaussian, score_type = "effective")
summary(mod)
```

## Negative Binomial

```{r,  message = FALSE}
set.seed(1)
D=data.frame(x=rnorm(40), z=rnorm(40))
D$y=rnbinom(40,mu=exp(-D$x),size=3)

library(MASS)
mod_par=glm.nb(y~x+z,data=D, link="log")
summary(mod_par)
mod=flipscores(y~x+z, data=D, family = "negbinom",score_type = "effective") 
summary(mod)
```



## References

J Hemerik, JJ Goeman and L Finos (2019) Robust testing in generalized linear models by sign-flipping score contributions, Submitted, arXiv: 1909.03796

<https://arxiv.org/abs/1909.03796>

## Bug reports
If you encounter a bug, please file a
[reprex](https://github.com/tidyverse/reprex) (minimal reproducible example)
on [github](https://github.com/livioivil/flipscores/issues).

## Bug reports
If you encounter a bug, please file a
[reprex](https://github.com/tidyverse/reprex) (minimal reproducible example)
on [github](https://github.com/livioivil/flipscores/issues).


