---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# Dev-version of the flipscores package
[On CRAN version](http://cran.r-project.org/web/packages/flipscores/index.html)


* * *

## Set up

To **install** this github version type (in R):

    ##if devtools is not installed yet: 
    ## install.packages("devtools") 
    library(devtools)
    install_github("livioivil/flipscores")


## References

J Hemerik, JJ Goeman and L Finos (2019) Robust testing in generalized
linear models by sign-flipping score contributions. Journal of the Royal
Statistical Society Series B: Statistical Methodology, Volume 82, Issue
3, July 2020, Pages 841–864.  
<https://doi.org/10.1111/rssb.12369>

R De Santis, J Goeman, J Hemerik, L Finos (2022) Inference in
generalized linear models with robustness to misspecified variances
arXiv: 2209.13918.  
<https://arxiv.org/abs/2209.13918>


## Some examples

```{r,  message = FALSE}
library(flipscores)
set.seed(1)
dt=data.frame(X=rnorm(20),
   Z=factor(rep(LETTERS[1:3],length.out=20)))
dt$Y=rpois(n=20,lambda=exp(dt$X))
mod=flipscores(Y~Z+X,data=dt,family="poisson",x=TRUE)
summary(mod)

# Anova test
anova(mod)
# or
mod0=flipscores(Y~Z,data=dt,family="poisson",x=TRUE)
anova(mod0,mod)
# and
mod0=flipscores(Y~X,data=dt,family="poisson")
anova(mod0,mod)

```

### Negative Binomial

```{r,  message = FALSE}
set.seed(1)
D=data.frame(x=(1:40)/20, z=rnorm(40))
D$y=rnbinom(40,mu=exp(D$x),size=3)

library(MASS)
mod_par=glm.nb(y~x+z,data=D, link="log")
summary(mod_par)
mod=flipscores(y~x+z, data=D, family = "negbinom") 
summary(mod)
```


## Bug reports
If you encounter a bug, please file a
[reprex](https://github.com/tidyverse/reprex) (minimal reproducible example)
on [github](https://github.com/livioivil/flipscores/issues).

